Every Author as First Author

### 2023-03-28 paper.tex
Document \namestack more
LaTeX code

%
% the following standard packages may be helpful, but are not required
%
%\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

%% OLD:
% Usage: \textstack{\textitem{item1}\textitem{item2}...}
\newcommand\textstack[1]{\strut\vbox to 0pt{\def\textstacksep{}#1}\ignorespaces}
\newcommand\textitem[1]{\textstacksep\hbox{\smash{#1}}\def\textstacksep{\vss}\ignorespaces}

\let\textstack=\relax

@@

\usepackage[final]{pdfcomment}
\usepackage{accsupp}

% Usage: \textstack{item1; item2; ...}
% Or: \textstack[sep]{item1 sep item2 sep ...}
% Expands to \vbox{\hbox{item1}\vskip-\baselineskip\hbox{item2}...},
% plus a PDF tooltip and copy/paste override with original text.
% Loop iteration based on https://tex.stackexchange.com/a/159177/245104
\makeatletter
\newcommand\textstack[2][;]{%
  % Append separator (#1) and \@eol to end of input:
  \def\textstack@append##1{\expandafter\textstack@step##1#1\@eol}%
  % Split into first component (##1) up to separator (#1), and rest (##2):
  \def\textstack@step##1#1##2\@eol{%
    \hbox{\ignorespaces ##1\unskip}%
    \ifx\@eol##2\@eol\else
      % More steps: unwind vertical space and continue
      \vskip-\baselineskip
      \textstack@step##2\@eol
    \fi}%
  % Tooltip with full author list
  \pdftooltip{%
    \BeginAccSupp{method=pdfstringdef,unicode,ActualText={#2}}%
      % Wrap stack in \vbox
      \vbox{\textstack@append{#2}}%
    \EndAccSupp{}%
  }{#2}%
}
% natbib support
\def\NAT@nmfmt#1{%
  \xdef\textstack@expand{#1}%
  \expandafter\namestack\textstack@expand
}
\makeatother

\usepackage{transparent}
\newcommand\namestack[2][0.666]{\texttransparent{#1}{\textstack{#2}}}

%%% Remove links from names so that tooltips are visible.
%%% Code from https://tex.stackexchange.com/a/27311/2451040

\usepackage{etoolbox}
\makeatletter

% Patch case where name and year are separated by aysep
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}

% Patch case where name and year are separated by opening bracket
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
       {\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}

\makeatother

@@

>>>>

%
% the following standard packages may be helpful, but are not required
%
%\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

% Theme based on https://tex.stackexchange.com/a/283543/245104
\usepackage{xcolor}
\definecolor{commentgreen}{RGB}{2,112,10}
%\definecolor{eminence}{RGB}{108,48,130}
%\definecolor{eminence}{RGB}{81,36,97} % 25% darker
\definecolor{ours}{RGB}{0,71,171} % cobolt blue
\definecolor{frenchplum}{RGB}{129,20,83}
\usepackage{listings}
\lstset{
  language=[LaTeX]TeX,
  basicstyle=\ttfamily,
  numbers=left, numberstyle=\footnotesize,
  commentstyle=\slshape\color{commentgreen},
  alsoletter={@},
  moretexcs={pdftooltip,BeginAccSupp,EndAccSupp,@eol,patchcmd,texttransparent,NAT@nmfmt,NAT@citex,NAT@hyper@,@citea,hyper@natlinkbreak,NAT@nm,NAT@aysep,NAT@spacechar,@citeb,@extra@b@citeb,NAT@date,NAT@@open},
  keywordstyle=\color{frenchplum},
  emph={textstack,textstack@step,textstack@append,textstack@expand,namestack},
  emphstyle=\color{ours}
  %texcsstyle=*\color{frenchplum}
}

%% OLD:
\iffalse
% Usage: \textstack{\textitem{item1}\textitem{item2}...}
\newcommand\textstack[1]{\strut\vbox to 0pt{\def\textstacksep{}#1}\ignorespaces}
\newcommand\textitem[1]{\textstacksep\hbox{\smash{#1}}\def\textstacksep{\vss}\ignorespaces}
\fi

@@

\input{namestack}
\input{stack-natbib}

@@

We implemented \LaTeX\ macros for easily superimposing author names
into an ``overlay stack''.
A user can build such a stack from a semicolon-separated list of names
like so:

\begin{center}
  \lstinline|\namestack{Erik Demaine; Martin Demaine}|

  $\to$ ~
  \namestack{Erik Demaine; Martin Demaine}
\end{center}

Listings \ref{lst:namestack} and \ref{lst:natbib}

\lstinputlisting[float=*,caption={\LaTeX\ source code for \texttt{\textbackslash namestack}},label=lst:namestack]{namestack.tex}
\lstinputlisting[float=*,caption={\LaTeX\ code providing additional support for \texttt{natbib.sty}},label=lst:natbib]{stack-natbib.tex}
